Predictors of frog survival following translocations - supplemental analyses

### 2023-03-10 code/translocation_survival_analysis.Rmd
Update and reorganize all analyses in Rmd files

---
title: "Predictors of frog survival following translocations - analyses"
author: "Roland Knapp"
output: html_notebook
---

The goal of the analyses in this notebook is to identify predictors of frog survival following translocation.
The analyses are conducted in a Bayesian framework using the R package rstanarm.

# Analysis 1: Site-level and frog-level predictors

## Load packages

```{r load-packages}
library(tidyverse)
library(brms)
library(rstanarm)
library(bayesplot)
library(tidybayes)
library(loo)
library(broom.mixed)
library(janitor)
library(patchwork)

@@

## Create frog translocation dataset for analysis

@@

```{r read-translocation-data}
d1 <- read_csv(here::here("data", "clean", "frog_translocation_final.csv")) %>% 
  drop_na(bd_load) %>%  # drop 12 records where bd_load is NA (9 are from 70413)
  mutate(
    first = if_else(order == 1, 1, 0),
    surv = if_else(survival < 0.5, 0, 1),
    male = if_else(sex == "m", 1, 0),
    elev_lo = if_else(elevation < 3020, 1, 0), # using interval defined by cut_interval, n = 2
    elev_z = arm::rescale(elevation),
    snowt_z = arm::rescale(snow_t),
    snowt1_z = arm::rescale(snow_t1),
    day_z = arm::rescale(day),
    length_z = arm::rescale(length),
    bdload_l = log10(bd_load + 1),
    bdload_z = arm::rescale(bdload_l),
    shore_c = shore - mean(shore),
    male_c = male - mean(male),
    elevlo_c = elev_lo - mean(elev_lo),
    first_c = first - mean(first),
    across(c(shore_c, male_c, elevlo_c, first_c), round, 3), 
    across(c(site_id, shore_c, first_c, donor, male_c, elevlo_c, year), as.factor),
    surv = as.integer(round(surv)))

@@

## Null values - check

```{r check-null}
d1 %>% summarize(across(everything(), ~ sum(is.na(.))))
```

## Model using non-standardized predictors

### Model specification

@@

## Explore a flat prior

We can explore a flat prior on the intercept using the code below.

@@

### Priors & chain diagnostics

@@

### List model variable names

@@

### Posterior predictive check

@@

### Calculate leave-one-out cross-validation (loo)

@@

### Posterior analysis

@@

-   Using non-standardized predictors makes plot hard to read due to vastly different scales of predictors.\
-   Based on 95% uncertainty intervals, important predictors are snow_t1, elevation, first, donor70567, and donor72996.

## Model using standardized predictors

### Model specification

@@

### Priors, chain diagnostics, posterior predictive check

@@

### Calculate loo

@@

## Compare models

@@

## Possible grouping structures to add to model

The dataset has three groups: site_id, translocation_id, and donor site.
Donor site is not suitable as a grouping variable because there are only 3 levels (i.e., site ids), not enough to make this useful.
Site_id and translocation_id contain 12 and 24 levels, respectively, making them suitable as grouping variables.
Including both site_id and translocation_id as nested grouping variables (i.e., translocations nested within site ids) also seems justified.
Having more levels within a group would seem to increase the power to detect effects of predictors.
With fewer levels/less variability, effect may be accounted for primarily by grouping variable itself instead of predictor.
With only 1-4 translocations per site and only 12 site ids total, it is possible that model with site_id as sole grouping variable and model with site_id and translocation_id as nested grouping variables will attribute more of the variation in frog survival to the grouping variables and less to the predictors.
A priori, that would suggest that the model with translocation_id as the grouping variable might be the most useful model structure (assuming that all models have similar posterior predictive accuracy).
Lacking any strong rationale for one model structure over another, built 3 models and compared their posterior predictive accuracy using loo.

## Model using standardized predictors and site_id grouping variable

### Model specification

@@

## Model using standardized predictors and translocation_id grouping variable)

### Model specification

@@

### Save plot

@@

## Model using standardized predictors and 2 grouping variables: translocation_id nested within site_id)

### Model specification

@@

## Compare 4 models with different grouping structures

@@

-   Based on expected log-predictive densities (ELPD), 3 models with grouping variables all have substantially higher posterior predictive accuracy than model without any grouping variables (elpd_diff of m1b is more than 2 SE lower than elpd_diff of m1c: elpd_diff = -18.2 $\pm$ 12.6, 2 SE interval does not overlap 0: -5.6 -- -30.8).
-   3 models with 1 or more grouping variables are equivalent and have similar posterior predictive accuracy (elpd_diff of m1e and m1d are within 2 SE of elpd_diff of m1c).\
-   m1d seems to provide more insight into the effect of the predictors, so chose this model for additional analysis.

## Additional analysis of model m1d

### Posterior classification accuracy

@@

-   Sensitivity or "true positive rate" measures the proportion of Y = 1 observations that are accurately classified.\
-   Specificity or "true negative rate" measures the proportion of Y = 0 observations that are accurately classified (i.e., proportion of frogs correctly identified as not surviving).

## Reduced model from m1d

### Create reduced model containing only important predictors for subsequent analyses

- Reduced model is helpful because it reduces the number of values used to calculate probabilities from predictive models.

@@

### Posterior analysis
```{r}
tidy(m1d_reduce, conf.int = TRUE, conf.level = 0.95)

@@

### Confirm that fit of reduced model is comparable to full model

@@

### Simulate and plot posterior predictive models & observations
#### Reduced model with translocation_id as grouping variable
```{r}
m1d_group_means <- d1 %>% 
  group_by(translocation_id) %>% 
  summarize(count = n(), psurv = mean(surv), elev_z = mean(elev_z), snowt1_z = mean(snowt1_z)) %>% 
  mutate(
    male_c = as.factor(0.548), 
    donor = case_when(
      str_detect(translocation_id, "74976") | str_detect(translocation_id, "70556") ~ "70459",
      str_detect(translocation_id, "70413") ~ "70567",
      TRUE ~ "72996")) %>% 
  arrange(psurv)  # to arrange plot values/labels by psurv

@@

#### Reduced model without grouping variable
To explore how addition of grouping variable affected predictions, especially that for 70370 and 70550. 
```{r}
m1d_reduce_nogroup <- stan_glm(
  surv ~ snowt1_z + elev_z + male_c + donor,
  data = d1,
  family = binomial,
  chains = 4, 
  iter = 5000*2, 
  cores = 4,
  seed = 84735)

@@

### Values of important predictors for translocations of interest
```{r}
d1 %>% 
  filter(site_id == "70370" | site_id == "70550") %>% 
  distinct(translocation_id, elevation, snow_t1, donor)

@@

### Plot posterior plausible relationships between each predictor and the probability of frog survival (conditional effects)

- As described in <https://rdrr.io/cran/brms/man/conditional_effects.brmsfit.html>, "When creating conditional_effects for a particular predictor (or interaction of two predictors), one has to choose the values of all other predictors to condition on. By default, the mean is used for continuous variables and the reference category is used for factors, but you may change these values via argument conditions. This also has an implication for the points argument: In the created plots, only those points will be shown that correspond to the factor levels actually used in the conditioning, in order not to create the false impression of bad model fit, where it is just due to conditioning on certain factor levels."\
-   Using rstanarm, I was unable to do this as I expected to: Start with data = d1 and using "newdata =" to specify that predictions should be based on data in d1_elevz (for example), in which non-plotted continuous predictors are set to the mean value. Not sure if my alternative approach is correct.\
-   Approach used: Instead of starting the routine with d1, I started with the new dataset in which all variables except the one of interest were set to mean values (continuous variables) and the reference level (categorical variables). This produced plots/results that were very similar to those produced in brms using the conditional_effects function.

#### Effect of elevation

@@

#### Effect of winter severity in year t1

@@

#### Effect of sex

@@

#### Effect of donor

@@

#### Joint effects of elevation and sex

@@

### Create multiplot conditional effects figure

@@

### Save plot

@@

## For comparison, fit model using brms and conditional_effects function to plot variable-specific effects

### Fit model

@@

### Plot conditional effects

@@

# Analysis 2: Survival of frogs from first translocation as predictor of survival in subsequent translocations

This analysis explores the results shown in translocation_survival_exploratory.Rmd (code chunk name = "frog-survival-by-site").
This plot shows frog survival of all translocations grouped by site, and indicates that survival is highly variable across sites, but repeatable within sites. The following analysis quantifies the association between survival in the first translocation and survival in subsequent translocations.

## Load packages

## Create frog translocation dataset for analysis

## Restructure dataset

## Model with non-standardized predictor, no grouping variable

### Model specification

### List model variable names

### Priors & chain diagnostics

### Posterior predictive check

### Calculate loo

### Posterior analysis

## Model with standardized predictors, no grouping variable

### Model specification

### List model variable names

### Priors & chain diagnostics

### Posterior predictive check

### Calculate loo

### Posterior analysis

### Save plot
```{r}
ggsave(here::here("doc", "manuscript", "figures", "mcmc_areas_m2b.png"), bg = "white", width = 7, height = 4)
```

## Model with standardized predictors, translocation_id grouping variable

### Model specification

### Priors & chain diagnostics

### Posterior predictive check

### Calculate loo

### Posterior analysis

## Model with standardized predictors, site_id grouping variable

### Model specification

### Priors & chain diagnostics

### Posterior predictive check

### Calculate loo

### Posterior analysis

### Compare 3 models with different grouping structures

-   Based on expected log-predictive densities (ELPD), models with and without grouping variables have similar posterior predictive accuracy (elpd_diff of m2b is less than 2 SE lower than elpd_diff of m2d: elpd_diff = -3.1 $\pm$ 5.8, 2 SE interval overlaps 0: 2.7 -- -8.9).\
-   Conclusion from all 3 models is the same: Average frog survival of first translocation is an important predictor of survival of individual frogs in subsequent translocations.

## Posterior classification accuracy of best models

## TO DO

-   Validate priors, tune as necessary. Add final priors to model specification (in case the defaults change).\
-   Check approach to plotting conditional effects.\
-   Try un-standardizing predictor values in conditional-effects plots (and other plots?) to produce more intuitive visualizations.

>>>>

---
title: "Predictors of frog survival following translocations - primary analyses"
author: "Roland Knapp"
output: html_notebook
---

The goal of these analyses is to identify predictors of frog survival following translocation.
The analyses are conducted in a Bayesian framework using the R package rstanarm.

## ANALYSIS 1: Effect of site on survival of all translocated cohorts

### Visualize survival across sites

#### Read in frog translocation dataset

```{r}
frog_translocation <- read_csv(here::here("data", "clean", "frog_translocation_final.csv")) %>% 
  mutate(site_id = as.character(site_id),
         donor = as.character(donor),
         surv = as.integer(if_else(survival < 0.5, 0, 1)))
```

#### Check for null values

```{r}
frog_translocation %>% summarize(across(everything(), ~ sum(is.na(.))))
```

-   12 records where bd_load is NA, no other NAs in dataset

#### Retrieve cohort-level frog survival data

```{r}
files <- fs::dir_ls(here::here("data", "raw", "cmr-analysis", "survival"), glob = "*_cohort.csv")
cohort_survival <- read_csv(files, id = "path") %>% 
  mutate(site_id = str_extract(path, "(\\d)+"), .after = path) %>%  # extracts site_id as numeric string from file path
  rename(years_since_intro = years_since_introduction) %>% 
  filter(years_since_intro == 1) %>% 
  select(site_id, release_date, years_since_intro, median_survival, lo_survival, hi_survival)
rm(files)
```

#### Plot of frog survival for each translocation - grouped by site and arranged by site-specific median survival

```{r}
palette1 <- c("green4", "blue", "black")

donors <- frog_translocation %>% 
  distinct(site_id, donor)

cohort_survival_plot <- cohort_survival %>% 
  mutate(release_year = year(release_date)) %>% 
  group_by(site_id) %>% 
  summarize(plot_survival = mean(median_survival)) %>%  # create variable by which to order sites for plotting
  arrange(plot_survival) %>% 
  mutate(siteid_order = row_number()) %>% 
  inner_join(cohort_survival, by = "site_id") %>% 
  inner_join(donors, by = "site_id") %>% 
  select(-plot_survival) %>%
  ggplot(aes(x = reorder(site_id, siteid_order), y = median_survival, color = donor)) +  # reorder site_id by siteid_order)
      geom_linerange(aes(ymin = lo_survival, ymax = hi_survival), color = "black", width = 0.5, position = position_dodge2(width=0.5)) +
      geom_point(aes(x = reorder(site_id, siteid_order), y = median_survival, color = donor), size = 3, position = position_dodge2(width=0.5)) + 
      scale_color_manual(values = palette1) + 
      labs(x = "Recipient site", y = "1-year frog survival") +
      theme_classic() +
      theme(
        legend.background = element_rect(color = "black", size = 0.3),
        legend.position = c(0.2, 0.8),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

cohort_survival_plot
```

-   Strong effect of site/translocation on frog survival.
-   Survival is highly variable across sites, but relatively invariant within a site.
-   Indicates need to include site_id and/or translocation_id as group-level effect(s).

#### Save plot

```{r}
ggsave(here::here("doc", "manuscript", "figures", "translocation_survival_bysiteid.png"), width = 5, height = 5) 
```

#### Plot of frog survival for each translocation - grouped by elevation

```{r}
frog_translocation %>%
  distinct(site_id, date, elevation) %>% 
  inner_join(cohort_survival, by = c("site_id", "date" = "release_date")) %>% 
    ggplot(aes(x = elevation, y = median_survival)) + 
      geom_vline(aes(xintercept = elevation), linetype = "dotted", color = "darkgray") +
      geom_point(size = 3) +
      geom_text(aes(label = site_id, x = elevation, y = 1.05), angle = 90) +
      coord_cartesian(ylim = c(0, 1.08)) +
      labs(x = "Elevation of recipient site", y = "1-year frog survival")
```

-   Elevation has a clear effect on frog survival, but there is a substantial amount of variation that remains unaccounted for.

### Model survival of frogs from first translocation as predictor of survival in subsequent translocations

-   This analysis explores the results shown in the plot created above (frog survival for all translocations grouped by site).

#### Load packages

@@

#### Create frog translocation dataset for analysis

@@

#### Restructure dataset

#### Model with non-standardized predictor, no grouping variable

##### Model specification

##### List model variable names

##### Priors & chain diagnostics

##### Posterior predictive check

##### Calculate loo

##### Posterior analysis

#### Model with standardized predictors, no grouping variable

##### Model specification

##### List model variable names

##### Priors & chain diagnostics

##### Posterior predictive check

##### Calculate loo

##### Posterior analysis

##### Save plot

```{r}
ggsave(here::here("doc", "manuscript", "figures", "mcmc_areas_m2b.png"), bg = "white", width = 7, height = 4)
```

#### Model with standardized predictors, translocation_id grouping variable

##### Model specification

##### Priors & chain diagnostics

##### Posterior predictive check

##### Calculate loo

##### Posterior analysis

#### Model with standardized predictors, site_id grouping variable

##### Model specification

##### Priors & chain diagnostics

##### Posterior predictive check

##### Calculate loo

##### Posterior analysis

#### Compare 3 models with different grouping structures

-   Based on expected log-predictive densities (ELPD), models with and without grouping variables have similar posterior predictive accuracy (elpd_diff of m2b is less than 2 SE lower than elpd_diff of m2d: elpd_diff = -3.1 $\pm$ 5.8, 2 SE interval overlaps 0: 2.7 -- -8.9).
-   Conclusion from all 3 models is the same: Average frog survival of first translocation is an important predictor of survival of individual frogs in subsequent translocations.

#### Posterior classification accuracy of best models

### TO DO

-   Validate priors, tune as necessary. Add final priors to model specification (in case the defaults change).

## ANALYSIS 2: Model of site-level and frog-level predictors

### Load packages

```{r}
library(tidyverse)
library(brms)
library(rstanarm)
library(bayesplot)
library(tidybayes)
library(loo)
library(broom.mixed)
library(janitor)
library(patchwork)

### Create frog translocation dataset for analysis

```{r}
d1 <- read_csv(here::here("data", "clean", "frog_translocation_final.csv")) %>% 
  drop_na(bd_load) %>%  # drop 12 records where bd_load is NA (9 are from 70413)
  mutate(
    first = if_else(order == 1, 1, 0),
    surv = if_else(survival < 0.5, 0, 1),
    male = if_else(sex == "m", 1, 0),
    elev_lo = if_else(elevation < 3020, 1, 0), # using interval defined by cut_interval, n = 2
    elev_z = arm::rescale(elevation),
    snowt_z = arm::rescale(snow_t),
    snowt1_z = arm::rescale(snow_t1),
    day_z = arm::rescale(day),
    length_z = arm::rescale(length),
    bdload_l = log10(bd_load + 1),
    bdload_z = arm::rescale(bdload_l),
    shore_c = shore - mean(shore),
    male_c = male - mean(male),
    elevlo_c = elev_lo - mean(elev_lo),
    first_c = first - mean(first),
    across(c(shore_c, male_c, elevlo_c, first_c), round, 3), 
    across(c(site_id, shore_c, first_c, donor, male_c, elevlo_c, year), as.factor),
    surv = as.integer(round(surv)))

@@

### Check for null values

```{r}
d1 %>% summarize(across(everything(), ~ sum(is.na(.))))
```

### Model using non-standardized predictors

#### Model specification

@@

#### Explore a flat prior on intercept

@@

#### Priors & chain diagnostics

@@

#### List model variable names

@@

#### Posterior predictive check

@@

#### Calculate leave-one-out cross-validation (loo)

@@

#### Posterior analysis

@@

-   Using non-standardized predictors makes plot hard to read due to vastly different scales of predictors.
-   Based on 95% uncertainty intervals, important predictors are snow_t1, elevation, first, donor70567, and donor72996.

### Model using standardized predictors

#### Model specification

@@

#### Priors, chain diagnostics, posterior predictive check

@@

#### Calculate loo

@@

#### Compare models

@@

### Model using standardized predictors and site_id grouping variable

#### Model specification

@@

### Model using standardized predictors and translocation_id grouping variable)

#### Model specification

@@

#### Save plot

@@

### Model using standardized predictors and 2 grouping variables: translocation_id nested within site_id)

#### Model specification

@@

### Compare 4 models with different grouping structures

@@

-   Based on expected log-predictive densities (ELPD), 3 models with grouping variables all have substantially higher posterior predictive accuracy than model without any grouping variables (elpd_diff of m1b is more than 2 SE lower than elpd_diff of m1c: elpd_diff = -18.2 $\pm$ 12.6, 2 SE interval does not overlap 0: -5.6 -- -30.8).
-   3 models with 1 or more grouping variables are equivalent and have similar posterior predictive accuracy (elpd_diff of m1e and m1d are within 2 SE of elpd_diff of m1c).
-   m1d seems to provide more insight into the effect of the predictors, so chose this model for additional analysis.

### Additional analysis of model m1d

#### Posterior classification accuracy

@@

-   Sensitivity or "true positive rate" measures the proportion of Y = 1 observations that are accurately classified.
-   Specificity or "true negative rate" measures the proportion of Y = 0 observations that are accurately classified (i.e., proportion of frogs correctly identified as not surviving).

### Reduced model from m1d

#### Create reduced model containing only important predictors for subsequent analyses

@@

#### Posterior analysis

```{r}
tidy(m1d_reduce, conf.int = TRUE, conf.level = 0.95)

@@

#### Confirm that fit of reduced model is comparable to full model

@@

#### Simulate and plot posterior predictive models & observations

##### Reduced model with translocation_id as grouping variable

```{r}
m1d_group_means <- d1 %>% 
  group_by(translocation_id) %>% 
  summarize(count = n(), psurv = mean(surv), elev_z = mean(elev_z), snowt1_z = mean(snowt1_z)) %>% 
  mutate(
    male_c = as.factor(0.548), 
    donor = case_when(
      str_detect(translocation_id, "74976") | str_detect(translocation_id, "70556") ~ "70459",
      str_detect(translocation_id, "70413") ~ "70567",
      TRUE ~ "72996")) %>% 
  arrange(psurv)  # to arrange plot values/labels by psurv

@@

##### Reduced model without grouping variable

To explore how addition of grouping variable affected predictions, especially that for 70370 and 70550.

```{r}
m1d_reduce_nogroup <- stan_glm(
  surv ~ snowt1_z + elev_z + male_c + donor,
  data = d1,
  family = binomial,
  chains = 4, 
  iter = 5000*2, 
  cores = 4,
  seed = 84735)

@@

##### Values of important predictors for translocations of interest

```{r}
d1 %>% 
  filter(site_id == "70370" | site_id == "70550") %>% 
  distinct(translocation_id, elevation, snow_t1, donor)

@@

#### Plot posterior plausible relationships between each predictor and the probability of frog survival (conditional effects)

-   All variables except the one of interest were set to mean values (continuous variables) and the reference level (categorical variables).

##### Effect of elevation

@@

##### Effect of winter severity in year t1

@@

##### Effect of sex

@@

##### Effect of donor

@@

##### Joint effects of elevation and sex

@@

##### Create multi-panel conditional effects figure

@@

##### Save plot

@@

#### For comparison, fit model using brms and conditional_effects function to plot variable-specific effects

##### Fit model

@@

##### Plot conditional effects

@@

### 2023-03-10 code/translocation_survival_analysis_suppl.Rmd
Update and reorganize all analyses in Rmd files

The supplemental analyses in this notebook provide additional details to analyses in `translocation_survival_analysis.Rmd`.

@@

```{r load-packages}
library(tidyverse)
library(brms)
library(rstanarm)
library(bayesplot)
library(tidybayes)
library(loo)
library(broom.mixed)
library(janitor)

@@

## Evaluate effect of frog size independent of donor population

-   Model m1d from `translocation_survival_analysis.Rmd` but using data subset where donor = 72996
-   Read in data, create variables for analysis, standardize continuous variables.
-   arm package used to rescale continuous variables (substract mean, divide by 2 SD), manual centering of binary variables.

## Assess effect on m1d of including all records, including where bd_load = NA

-   Read in data, create variables for analysis, standardize continuous variables.
-   arm package used to rescale continuous variables (substract mean, divide by 2 SD), manual centering of binary variables.

## Analysis of changes in Bd load following translocation

@@

```{r read-data}
translocation <- read_csv(here::here("data", "raw", "frog_translocation.csv")) %>% 
  relocate(visit_date = release_date, .before = type) %>% 
  rename(survey_type = type) %>% 
  mutate(pit_tag_ref = replace(pit_tag_ref, pit_tag_ref == "900067000117396" & site_id == 70641, "111111111111111")) %>% # remove incorrect pit_tag_ref identified in translocation_survival_createdata.Rmd
  filter(pit_tag_ref != "111111111111111")

@@

-   site_id: Unique 5-digit site identifier.\
-   site_id1: Assigned 5-digit site identifier for a collection of adjacent sites that are utilized by a frog population.
-   translocation_id: Unique identifier for each translocation.\
-   visit_date: Date on which translocation or survey was conducted.\
-   survey_type: "translocation" or "cmr".\
-   period: "before" or "after" translocation.
-   year_translocate: Year in which translocation was conducted.\
-   year_capture: Year in which frog was captured.\
-   interval: Number of years between translocation and frog capture.\
-   pit_tag_ref: Unique PIT tag identifier.\
-   swab_id: Unique identifier for skin swab sample.\
-   bd_load: Bd infection intensity determined from skin swab samples, units are number of ITS1 copies \* 80.

@@

@@

#### Null values - check

@@

## Calculate parameters for viability analysis

@@

-   Assumptions:

@@

-   Assume that

>>>>

The following are supplemental analyses, some related to analyses in `translocation_survival_analysis.Rmd` and some unrelated.

@@

```{r}
library(tidyverse)
library(brms)
library(rstanarm)
library(bayesplot)
library(tidybayes)
library(loo)
library(broom.mixed)
library(janitor)

@@

## ANALYSIS 1: Analysis of changes in Bd load following translocation

@@

```{r}
translocation <- read_csv(here::here("data", "raw", "frog_translocation.csv")) %>% 
  relocate(visit_date = release_date, .before = type) %>% 
  rename(survey_type = type) %>% 
  mutate(pit_tag_ref = replace(pit_tag_ref, pit_tag_ref == "900067000117396" & site_id == 70641, "111111111111111")) %>% # remove incorrect pit_tag_ref identified in translocation_survival_createdata.Rmd
  filter(pit_tag_ref != "111111111111111")

@@

-   site_id: Unique 5-digit site identifier.
-   site_id1: Assigned 5-digit site identifier for a collection of adjacent sites that are utilized by a frog population.
-   translocation_id: Unique identifier for each translocation.
-   visit_date: Date on which translocation or survey was conducted.
-   survey_type: "translocation" or "cmr".
-   period: "before" or "after" translocation.
-   year_translocate: Year in which translocation was conducted.
-   year_capture: Year in which frog was captured.
-   interval: Number of years between translocation and frog capture.
-   pit_tag_ref: Unique PIT tag identifier.
-   swab_id: Unique identifier for skin swab sample.
-   bd_load: Bd infection intensity determined from skin swab samples, units are number of ITS1 copies \* 80.

@@

-   Model with pit_tag_ref grouping variable is the model of primary interest, roughly analogous to paired t-test. Included other models to allow a better understanding of the data.

@@

#### Check for null values

@@

-   All models are equivalent, so pairing before-after by pit_tag_ref is unimportant.

## ANALYSIS 2: Evaluate effect of frog size independent of donor population

-   Model m1d from `translocation_survival_analysis.Rmd` but using data subset where donor = 72996 only.

-   arm package used to rescale continuous variables (substract mean, divide by 2 SD), manual centering of binary variables.

## ANALYSIS 3: Assess effect on m1d of including all records, including where bd_load = NA

-   Additional analysis of model m1d from `translocation_survival_analysis.Rmd`.

-   arm package used to rescale continuous variables (substract mean, divide by 2 SD), manual centering of binary variables.

## ANALYSIS 4: Calculate parameters for viability analysis

@@

Assumptions:

@@
